\documentclass[11pt,a4paper]{article}
\usepackage[margin=2.2cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{fontspec}
\usepackage{xeCJK}
% Korean glyphs (KCI journal title/venue below) need a CJK-capable font.
% Prefer the system font on macOS (Apple SD Gothic Neo); fall back to
% Noto CJK on Linux CI runners (installed via `apt-get install fonts-noto-cjk`).
\IfFontExistsTF{Apple SD Gothic Neo}{%
  \setCJKmainfont{Apple SD Gothic Neo}
}{%
  \IfFontExistsTF{Noto Serif CJK KR}{%
    \setCJKmainfont{Noto Serif CJK KR}
  }{%
    \setCJKmainfont{Noto Sans CJK KR}
  }
}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[colorlinks=true,linkcolor=black,urlcolor=black,citecolor=black]{hyperref}
\usepackage{xurl} % allow long DOI/URL text to break at any character (avoids overfull hboxes)
\usepackage{xcolor}

\titleformat{\section}{\Large\bfseries}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{6pt}{2pt}
\pagestyle{plain}
\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist{topsep=0pt,itemsep=1pt,parsep=0pt}

\begin{document}

\begin{center}
{\LARGE\bfseries Yeonchan Kang}\\[6pt]
Ph.D.\ Student in Economics, Sungkyunkwan University\\[4pt]
\href{mailto:nanyeon99@g.skku.edu}{nanyeon99@g.skku.edu} ~$\cdot$~ \href{mailto:nanyeon99@gmail.com}{nanyeon99@gmail.com}\\
\href{https://nanyeonk.github.io}{nanyeonk.github.io} ~$\cdot$~ ORCID: \href{https://orcid.org/0009-0004-5988-299X}{0009-0004-5988-299X}
\end{center}

\section{Profile}

Ph.D.\ student in Economics at Sungkyunkwan University. My current research agenda focuses on housing and commercial real-estate markets, using big data, econometrics, and machine learning for property valuation and local market analysis. This work builds on my earlier research in empirical asset pricing, portfolio choice, and financial machine learning.

\section{Education}

\textbf{Sungkyunkwan University} \hfill 2026--present\\
Ph.D.\ in Economics

\textbf{Sungkyunkwan University} \hfill 2026\\
M.A.\ in Economics\\
Thesis: ``Factor Timing with Characteristic-State Similarity'' \textbar{} Advisor: Doojin Ryu

\textbf{Inha University} \hfill 2024\\
B.S.\ in Industrial Engineering

\section{Research Interests}

Commercial Real Estate ~$\cdot$~ Housing Markets ~$\cdot$~ Asset Pricing ~$\cdot$~ Portfolio Choice ~$\cdot$~ Big Data \& Machine Learning

\section{International Refereed Journals (SSCI)}

\begin{enumerate}[leftmargin=1.5em]
\item Kang, Y., \& Ryu, D. (Conditionally Accepted, 2026). ``Factor Timing with Characteristic-State Similarity.'' \textit{Journal of Portfolio Management}. (SSCI)
\item Kang, Y., \& Ryu, D. (2026). ``Time-Series Momentum and Market-Timing in Bitcoin.'' \textit{Risk Management}, 28, 54. \url{https://doi.org/10.1057/s41283-026-00234-7}. (SSCI)
\item Kang, H., Kang, Y., Ryu, D., \& Webb, R. I. (2026). ``Bitcoin Forecasting with Machine Learning and On-Chain Information.'' \textit{Investment Analysts Journal}. \url{https://doi.org/10.1080/10293523.2026.2616575}. (SSCI)
\item Kang, Y., Ryu, D., \& Webb, R. I. (2026). ``Uncertainty Indicators as Key Predictors of Oil Volatility: An Interpretable Machine Learning Approach.'' \textit{Computational Economics}. \url{https://doi.org/10.1007/s10614-025-11299-z}. (SSCI)
\item Kang, Y., Ryu, D., \& Webb, R. I. (2025). ``How Well Do Machine Learning Models in Finance Work?'' \textit{Financial Innovation}, 11. \url{https://doi.org/10.1186/s40854-025-00870-0}. (SSCI)
\item Bang, J., Kang, Y., \& Ryu, D. (2024). ``Potential Pricing Factors in the Korean Market.'' \textit{Finance Research Letters}, 67. \url{https://doi.org/10.1016/j.frl.2024.105946}. (SSCI)
\end{enumerate}

\section{Domestic Refereed Journals (KCI)}

\begin{enumerate}[leftmargin=1.5em]
\item Kang, Y., \& Ryu, D. (2023). ``Trends in the Application of Machine Learning Models in Finance'' [금융 분야의 기계학습 모형 활용 추이]. \textit{금융공학연구}. (KCI)
\end{enumerate}

\section{Working Papers}

\begin{itemize}[leftmargin=1.5em]
\item Kang, Y., \& Ryu, D. (Revise and Resubmit, 2026). ``One City, Multiple Markets: District-Specific Housing Valuations Using Interpretable Machine Learning.'' \textit{Spatial Economic Analysis}. (SSCI)
\item Kang, Y., \& Ryu, D. (Under Review, 2026). ``Market-specific confirmation horizons in momentum turning-point strategies.'' \textit{Applied Economics}. (SSCI)
\end{itemize}

\section{Work in Progress}

\begin{itemize}[leftmargin=1.5em]
\item ``Representing Location in House-Price Prediction: Hexagonal Spatial Encodings and Out-of-Sample Performance''
\item ``Private Education Capitalization in Seoul Housing and Jeonse Markets''
\item ``Temporal Demand Structure and Shopping District Rent Capitalization''
\end{itemize}

\section{Awards \& Fellowships}

\textbf{Korean Finance Association -- Kiwoom Securities Ph.D. Fellowship} \hfill Recipient, 2026--2027\\
\textbf{Best Paper Award}, Korean Financial Management Association \hfill 2025\\
\textbf{BK21 Fellowship}, Sungkyunkwan University, Master's Program \hfill 2024--2025\\
\textbf{BK21 Fellowship}, Sungkyunkwan University, Ph.D. Program \hfill Recipient, 2026--2027

\section{Conference Presentations}

\begin{itemize}[leftmargin=1.5em, nosep]
\item Korea's Allied Economic Associations Annual Meeting, Financial Engineering Session \hfill February 2026
\item Korean Financial Management Association Annual Conference \hfill November 2025
\item Asia-Pacific Association of Finance International Conference \hfill July 2025
\item SERI International Conference \hfill July 2025
\item Seoul Workshop on Empirical Finance \hfill May 2025
\item Korean Financial Management Association Annual Conference \hfill November 2024
\item SERI International Conference \hfill July 2024
\item Korea's Allied Economic Associations Annual Meeting \hfill February 2024
\end{itemize}

\section{Skills}

\textbf{Econometrics:} Panel data, hedonic pricing\\
\textbf{Machine Learning (including DL):} Tabular prediction with panel structures, interpretability (SHAP, PFI, PDP), image-based analysis, text mining, ensemble methods\\
\textbf{Programming:} R (fixest, tidyverse), Python (scikit-learn, PyTorch), DuckDB, SQL\\
\textbf{Tools:} \LaTeX, Git

\section{Languages}

Korean (native) ~$\cdot$~ English (proficient)

\section{Military Service}

\textbf{Republic of Korea Army}, CBRN Specialist \hfill 2019--2021

\section{References}

\href{https://sites.google.com/view/ryudoojin}{\textbf{Doojin Ryu}}\\
Professor of Economics, Sungkyunkwan University

\href{https://www.commerce.virginia.edu/faculty/riw4j}{\textbf{Robert I.\ Webb}}\\
Professor of Finance, University of Virginia

\end{document}
